### 2014-10-01 tex/proofs.tex
Slight retool to focus on deriving the representation relation.

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation as defined in
\eqref{eqn:BisimulationForwards} and
\eqref{eqn:BisimulationBackwards}. This proof is accomplished by
showing that the requisite homomorphism, $\rightharpoonup_h$, used in
the representation relation exists. A bisimulation is a relation over
pairs of states such that whenever two states, $s_\ell$ and
$s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
s_\varsigma$, every successor, from either state, $s_\ell
\rightarrow_\ell s_\ell^\prime$ or $s_\varsigma \rightarrow_\varsigma
s_\varsigma^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $s_\ell^\prime \sqsubset s_\varsigma^\prime$.

@@

The proof of the representation relation as a bisimulation reasons
over individual rules in the $\varsigma$-relation to show that each
rule preserves exactness. That is to say that whenever the state on
the left of the $\varsigma$-relation has a corresponding state that it
represents in the $\ell$-relation, its successor set is both sound and
complete relative the $\ell$-relation and subject to the
representation relation. Intuitively, the $\varsigma$-relation, at a
given state, has a successor to account for every successor from the
$\ell$-relation at the corresponding state, and the $\ell$-machine has
a successor to account for every successor in the
$\varsigma$-relation.

The proof of exactness of each rule relies on the ability to derive
from the homomorphism in the representation relation in the current
state, a new homomorphism that is sufficient to use in the
representation relation that includes the successor states. The proof
is constructive in that it shows how given a valid homomorphism for
the current state, it is possible to derive a new homomorphism that
includes successor states.

There are two slight complications in the proof: the field access rule
relies on the $S$-relation that operates on a different state that
then $\varsigma$-relation and constructing the new homomorphism in the
equals-reference rule relies on the incoming heap being location
mutual exclusive. The $S$-relation effectively produces an
intermediary state that is the state where uninitialized references
are initialized before the field access actually takes place. In
essence, a state on the left of the $\varsigma$-relation that is a
field access, undergoes a transition in which its heap is changed to
initialize fields. Once the fields are initialized, then the actual
field access takes place. The state with the heap that has the
initialized fields is the intermediary state between the state on the
left of the $\varsigma$-relation and the state on the right of the
$\varsigma$-relation. The proof reasons separately about this
intermediary state to prove that it too is exact.

>>>>

The goal of this section is to prove that the representation relation,
$\sqsubset$, is a bisimulation as defined in
\eqref{eqn:BisimulationForwards} and
\eqref{eqn:BisimulationBackwards}.  A bisimulation is a relation over pairs of states such that whenever two states, $s_\ell$ and
$s_\varsigma$, are related in the bisimulation, $s_\ell \sqsubset
s_\varsigma$, every successor, from either state, $s_\ell
\rightarrow_\ell s_\ell^\prime$ or $s_\varsigma \rightarrow_\varsigma
s_\varsigma^\prime$, has a corresponding mutual successor in the other
state such that both of those successors are also related in the
bisimulation: $s_\ell^\prime \sqsubset s_\varsigma^\prime$.

@@

The proof of the representation relation as a bisimulation reasons
over individual rules in the $\varsigma$-relation to show that for
each rule, the representation relation, $\sqsubset$, exists; thus, the
representation relation is a bisimulation for the system consisting
only of the rule in consideration. Whenever the state on the
left of the $\varsigma$-relation has a corresponding state that it
represents in the $\ell$-relation, its successor set is both sound and
complete relative the $\ell$-relation under the new
representation relation that now includes the successors.

The heart of the representation relation is the homomorphism that maps
locations in one heap to locations in the other heap. The proof
reasons over of each rule and as mentioned previously, and derives
from the current homomorphism in the representation relation for the
current states, a new homomorphism that is sufficient to use in the a
new representation relation that includes the successor states. The
proof is constructive in that it shows how given a valid homomorphism
for the current states, it is possible to derive a new homomorphism
that includes successor states. With such a new homomorphism, it is
possible to state that for the $\varsigma$-relation, when restricted
to a specific rule (i.e., that is the only rule available in the
relation), the representation relation is a bisimulation for that
restricted $\varsigma$-relation. If such a bisimulation exists for all
the individual rules, then it exists for the rules collectively.

There are two slight complications in the proof: first, the field access rule
relies on the $S$-relation that operates on a different state 
than then $\varsigma$-relation; and second, constructing the new homomorphism in the
equals-reference rule relies on the incoming heap being location
mutual exclusive. The $S$-relation effectively produces an
intermediary state that is the state where uninitialized references
are initialized before the field access actually takes place. In
essence, a state on the left of the $\varsigma$-relation that is a
field access, undergoes a transition in which its heap is changed to
initialize fields. Once the fields are initialized, then the actual
field access takes place. The state with the heap that has the
initialized fields is the intermediary state between the state on the
left of the $\varsigma$-relation and the state on the right of the
$\varsigma$-relation. The proof reasons separately about this
intermediary state to prove that it too is exact.
